Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-18 paper/paper.tex
Describe economic situations #51

\subsection{Economic Situations}
% Summarize King 2001: 535-538

Information is scant on economic conditions in Nagorno-Karabakh since the 1994 ceasefire. 
International Crisis Group (2005: 14--15) provides a rare account of Karabakh's economy as follows. 
\begin{itemize}
\item Entrepreneurs have been engaged in profitable scrap metal businesses by dismantling infrastructure, housing and other pre-war structures for the resale of metal, bricks and building materials in the occupied territory of Azerbaijan.
\item Privatization of land and state enterprises has largely been completed. All residents outside the capital city of Stepanakert received 0.6 hectares of arable land. Private companies account for 80\% of the output. 
\item Under-employment is widespread among rural residents although officials claim that the unemployment rate was 5.6\% in 2003. In 2005, the government started providing the unemployed with 60\% of the minimum wage.
\item The government encourages child birth through various benefits for children: large families receive free electricity and books; couples with three children or more receive cash grants; and those with six children or more are given new homes.
\item Income inequality is growing. In a survey of 1,000 by Stepanakert Press Club in October 2003, 40.5\% of the respondents answered that they lived better than five years ago while 57.6\% said their life got worse or didn't change.
\end{itemize}

On the other hand, Azerbaijan proper has experienced economic growth thanks to oil exports. 
In 2006, the oil pipeline was opened from Baku, the capital city, to Turkey via Georgia, contributing to the world's fastest economic growth from 2005 to 2008 (de Waal 2013: 291--292). 
World Bank (2006: Table 1) reports that the percentage of people living in poverty fell from 44.6\% in 2002 to 24.0\% in 2005.
This rapid decline is not concentrated in Baku and other urban areas but also seen in rural areas.

 \subsection{Abkhazia}
 International Alert (2004: 123) reports that GDP per capita in Abkhazia was roughly estimated to be \$350 in 2001, dropped from \$1333 in 1988, with the population dependent on subsistence farming and humanitarian aid for survival.

 \subsection{South Ossetia}
 Areshidze (2002), cited by International Crisis Group (2004: 11), estimates that GDP per capita in South Ossetia was \$250 in 2002.

>>>>

\subsection{Economic Situations}
% Summarize King 2001: 535-538
There is only sketchy information on economic situations in the four unrecognized states. King (2001: 535-538) reports one of the rare accounts, based on his own interviews with local residents in 2000.

Residents in Nagorno-Karabakh earned a living from subsistence farming or resale of goods imported from Iran and Armenia, with the export of wood to Armenia becoming a booming business.

In Abkhazia, important sources of revenue for residents are the harvesting of tangerines and hazelnuts and trade in scrap metal.

South Ossetia had little functioning industry or export-oriented agriculture, with thriving trade activities along the highway linking Georgia to the south with Russia to the north.

Transnistria, the industrial hub of Moldova during the Soviet era with one of the best steel mills in the Soviet Union, ``exported'' construction materials, chemicals, ferrous metals, and electrical energy to Moldova proper, and steel and small arms to the world.

%Information is scant on economic conditions in Nagorno-Karabakh since the 1994 ceasefire. 
%International Crisis Group (2005: 14--15) provides a rare account of Karabakh's economy as follows. 
%\begin{itemize}
%\item Entrepreneurs have been engaged in profitable scrap metal businesses by dismantling infrastructure, housing and other pre-war structures for the resale of metal, bricks and building materials in the occupied territory of Azerbaijan.
%\item Privatization of land and state enterprises has largely been completed. All residents outside the capital city of Stepanakert received 0.6 hectares of arable land. Private companies account for 80\% of the output. 
%\item Under-employment is widespread among rural residents although officials claim that the unemployment rate was 5.6\% in 2003. In 2005, the government started providing the unemployed with 60\% of the minimum wage.
%\item The government encourages child birth through various benefits for children: large families receive free electricity and books; couples with three children or more receive cash grants; and those with six children or more are given new homes.
%\item Income inequality is growing. In a survey of 1,000 by Stepanakert Press Club in October 2003, 40.5\% of the respondents answered that they lived better than five years ago while 57.6\% said their life got worse or didn't change.
%\end{itemize}

%On the other hand, Azerbaijan proper has experienced economic growth thanks to oil exports. 
%In 2006, the oil pipeline was opened from Baku, the capital city, to Turkey via Georgia, contributing to the world's fastest economic growth from 2005 to 2008 (de Waal 2013: 291--292). 
%World Bank (2006: Table 1) reports that the percentage of people living in poverty fell from 44.6\% in 2002 to 24.0\% in 2005.
%This rapid decline is not concentrated in Baku and other urban areas but also seen in rural areas.

% \subsection{Abkhazia}
%International Alert (2004: 123) reports that GDP per capita in Abkhazia was roughly estimated to be \$350 in 2001, dropped from \$1333 in 1988, with the population dependent on subsistence farming and humanitarian aid for survival.

 %\subsection{South Ossetia}
%Areshidze (2002), cited by International Crisis Group (2004: 11), estimates that GDP per capita in South Ossetia was \$250 in 2002.
